### 2021-01-04 tex/paper.tex
Fix spelling.
Add Simplifier and Mendix setup.

@@

In \cref{fig:corteza_home_screen}, we can see the initial screen of the Corteza platform. By selecting “Low Code”, we reach a new view containing all existing “Low Code Namespaces”. A namespace can be thought of as an individual application within the low-code environment. In order to start with our application, we create a \texttt{todo-list} namespace. Next we need to create a module. A module in Corteza is similar to creating a database schema for a single table. For our application, we create a module containing text fields for \texttt{title} and \texttt{body} and a dropdown field for the \texttt{status}. We also mark \texttt{title} as a required field, as seen in \cref{fig:corteza_module}. Next, we need to create a page which lets us add TODOs to our list. To do this, we create a blank page and add the pre-built “Record List” block. In the “Record List” block, we select our “Todo Module” as the data source and select all fields so they are displayed in the list. The list also provides an option to allow inline editing of records. Without this option, the user has to click on the list item to open the detail page in order to edit it. Unfortunately, for some reason when enabling the checkbox to allow inline editing, we were unable to save the page with this configuration. Nevertheless, the basic functionality of our application was completely implemented in less than ten minutes.

>>>>

\subsubsection{Simplifier}

Simplifier is, like Oracle APEX, a web-based application development environment on low-code basis. Simplifier offers a demo platform called “Simplifier Playground”, an instance of the Simplifier platform specifically set up for trialling the platform. The trial instance is reset to defaults every night, so all data stored on it will not be persisted. They also offer a “Freemium” instance, available by registering via an email address, which has no such limitation, we therefore applied for such an instance. %TODO

\subsubsection{Mendix}

Similar to Oracle APEX and Simplifier, Mendix is also a web-based environment for low-code application development. Mendix offerse a free tier which allows hosting unlimited applications with 1GB of memory and 0.5GB of storage per application. For more advanced needs, Mendix offers an enterprise option starting at 1875€ per month, allowing on-premises hosting and hosting on private clouds, e.g. AWS, IBM etc. For our evaluation purposes, the free tier is more than enough given there are no restrictions on the provided functionality. Creating an account was straight-forward and we were able to log in within minutes of registering. There are two options for developing applications using Mendix: The first is the web-based environment called Mendix Studio, the second a native desktop application called Mendix Studio Pro, offering more advanced options for professional users. Unfortunately Mendix Studio Pro is only available for Microsoft Windows, so we were not able to test it, the basic functionality for creating low-code application is the same in both versions of Mendix Studio, however.

@@

In \cref{fig:corteza_home_screen}, we can see the initial screen of the Corteza platform. By selecting “Low Code”, we reach a new view containing all existing “Low Code Namespaces”. A namespace can be thought of as an individual application within the low-code environment. In order to start with our application, we create a \texttt{todo-list} namespace. Next we need to create a module. A module in Corteza is similar to creating a database schema for a single table. For our application, we create a module containing text fields for \texttt{title} and \texttt{body} and a drop-down field for the \texttt{status}. We also mark \texttt{title} as a required field, as seen in \cref{fig:corteza_module}. Next, we need to create a page which lets us add TODOs to our list. To do this, we create a blank page and add the pre-built “Record List” block. In the “Record List” block, we select our “Todo Module” as the data source and select all fields so they are displayed in the list. The list also provides an option to allow inline editing of records. Without this option, the user has to click on the list item to open the detail page in order to edit it. Unfortunately, for some reason when enabling the checkbox to allow inline editing, we were unable to save the page with this configuration. Nevertheless, the basic functionality of our application was completely implemented in less than ten minutes.
